Supplementary Materials for: The promise of community-driven preprints in ecology and evolution

### 2024-10-15 docs/supp.qmd
Open access status too

Data from each preprint was cross checked by one additional author to ensure accuracy and consistency of the data collected. Any discrepancies were either discussed or fixed prior to analysis. Most data that was corrected included data such as missed DOI's for published preprints, missing or incorrect citation counts to preprints and published articles, and missing or incorrect publication dates. It became evident that missing citation counts to preprints were largely the result of preprints and published articles not being correctly merged in Google Scholar. As such, checking citations to preprints involved looking carefully at all papers on the submitting author's Google Scholar profile and cross checking titles. Often it was clear redundant articles existed that were not merged. We then checked that the unmerged preprint and the published article were in fact the same study before updating preprint and publication citation counts. We also made note when any titles changed from preprint to publication. At times, preprints had been merged with published versions of the same study. To cross-check citation count to the preprint itself, we looked at the version history of the publication. If we found a clear preprint version, we took the citation count from that version. If it was not provided we assumed no data existed on citation counts for the preprint and it was assigned 'NA'.

As indicated in the main manuscript. We collected data on the ‘academic age’ of submitting authors by looking at Google Scholar profiles of authors (when available) and recording their first year of publication in a peer-reviewed journal. If no google Scholar profile for the submitting author was availabel we attempted to acquire the information from other online research profiles (e.g., ResearchGate, ORCID, etc.). If no information was available we entered '0' as the first year of publication.

@@

>>>>

Data from each preprint was cross checked by one additional author to ensure accuracy and consistency of the data collected. Any discrepancies were either discussed or fixed prior to analysis. Most data that was corrected included data such as missed DOI's for published preprints, missing or incorrect citation counts to preprints and published articles, and missing or incorrect publication dates. It became evident that missing citation counts to preprints were largely the result of preprints and published articles not being correctly merged in Google Scholar. As such, checking citations to preprints involved looking carefully at all papers on the submitting author's Google Scholar profile and cross checking titles. Often it was clear redundant articles existed that were not merged. We then checked that the unmerged preprint and the published article were in fact the same study before updating preprint and publication citation counts. We also made note when any titles changed from preprint to publication. At times, preprints had been merged with published versions of the same study. To cross-check citation count to the preprint itself, we looked at the version history of the publication. If we found a clear preprint version, we took the citation count from that version. If it was not provided we assumed no data existed on citation counts for the preprint and it was assigned 'NA'. As indicated in the main manuscript. We collected data on the ‘academic age’ of submitting authors by looking at Google Scholar profiles of authors (when available) and recording their first year of publication in a peer-reviewed journal. If no google Scholar profile for the submitting author was available we attempted to acquire the information from other online research profiles (e.g., ResearchGate, ORCID, etc.). If no information was available we entered '0' as the first year of publication.

## Data collected computationally

@@

The open access status of each published article was obtained using the R package *roadoi* (v.`r utils::packageVersion("roadoi")`) to connect to the Unpaywall platform [@jahn2024]. This R package provided data on whether the published article was open access or not (i.e., whether the article was behind a paywall or not), and categorized the open access status of teh article (Sub-type meanings included: ‘Green’, articles published in ‘toll-access journals but achieved in an open access repository; ‘Bronze’, articles are free to read on publishers website without a license but grants no other rights and can be delayed free-to-read; ‘Hybrid’, articles are free to read upon publication with an open access license; ‘Gold’, articles published in fully open access journals. For full details on the meaning of each category see  https://support.unpaywall.org/support/solutions/articles/44001777288-what-do-the-types-of-oa-status-green-gold-hybrid-and-bronze-mean- ).
